Calibration of P-values for calibration and for deviation of a subpopulation from the full population

### 2023-04-08 tex/paper.tex
weighted average

In order to gauge deviation of the observed responses
$R_1$,~$R_2$, \dots, $R_n$ from the given function $r$,
we construct the sequence of cumulative differences
%
\begin{equation}
B_{\ell} = \frac{\sum_{k=1}^{\ell} (R_k - r(S_k)) \, W_k}{\sum_{k=1}^n W_k}
\end{equation}
%
for $\ell = 1$,~$2$, \dots, $n$.
We also construct the sequence of cumulative weights
%
\begin{equation}
A_{\ell} = \frac{\sum_{k=1}^{\ell} W_k}{\sum_{k=1}^n W_k}
\end{equation}
%
for $\ell = 1$,~$2$, \dots, $n$.
Figures~\ref{la}, \ref{stanislaus}, and~\ref{napa}
of Subsection~\ref{analysis} below plot $B_1$,~$B_2$, \dots, $B_n$
versus $A_1$,~$A_2$, \dots, $A_n$ for some numerical examples.
A simple calculation of~\citet{tygert_full} shows that the expected slope
of the line graph of $B_1$,~$B_2$, \dots, $B_n$ versus 
$A_1$,~$A_2$, \dots, $A_n$ from $A_{k-1}$ to $A_k$ is $\E[R_k] - r(S_k)$;
that is, the expected slope is simply the deviation of the expected response
from the full population's, in a graph for which $A_1$,~$A_2$, \dots, $A_n$
are the abscissae (the horizontal coordinates) and $B_1$,~$B_2$, \dots, $B_n$
are the ordinates (the vertical coordinates).
Thus, steep slope over a long range indicates
significant average deviation over that range.
Indeed, the slope of the secant line connecting two points on the graph becomes
the average deviation over the long range of scores between those points.

>>>>

In order to gauge deviation of the observed responses
$R_1$,~$R_2$, \dots, $R_n$ from the given function $r$,
we construct the sequence of cumulative differences
%
\begin{equation}
B_{\ell} = \frac{\sum_{k=1}^{\ell} (R_k - r(S_k)) \, W_k}{\sum_{k=1}^n W_k}
\end{equation}
%
for $\ell = 1$,~$2$, \dots, $n$.
We also construct the sequence of cumulative weights
%
\begin{equation}
A_{\ell} = \frac{\sum_{k=1}^{\ell} W_k}{\sum_{k=1}^n W_k}
\end{equation}
%
for $\ell = 1$,~$2$, \dots, $n$.
Figures~\ref{la}, \ref{stanislaus}, and~\ref{napa}
of Subsection~\ref{analysis} below plot $B_1$,~$B_2$, \dots, $B_n$
versus $A_1$,~$A_2$, \dots, $A_n$ for some numerical examples.
A simple calculation of~\citet{tygert_full} shows that the expected slope
of the line graph of $B_1$,~$B_2$, \dots, $B_n$ versus 
$A_1$,~$A_2$, \dots, $A_n$ from $A_{k-1}$ to $A_k$ is $\E[R_k] - r(S_k)$;
that is, the expected slope is simply the deviation of the expected response
from the full population's, in a graph for which $A_1$,~$A_2$, \dots, $A_n$
are the abscissae (the horizontal coordinates) and $B_1$,~$B_2$, \dots, $B_n$
are the ordinates (the vertical coordinates).
Thus, steep slope over a long range indicates
significant weighted average deviation over that range.
Indeed, the slope of the secant line connecting two points on the graph becomes
the weighted average deviation over the long range of scores
between those points.
